# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data

Loading the data:
```{r}
library(lattice)
activity <- read.csv('activity.csv')
                     
```
Preprocessing:
```{r}
activ_complete <- activity[complete.cases(activity),]
```



## What is mean total number of steps taken per day?
```{r}
stepsperday <- aggregate(activ_complete$steps,list(Date = activ_complete$date), sum)
hist(stepsperday$x, xlab='Steps per Day', main='Histogram of Steps per Day')
```

Mean total number of steps taken per day:
```{r}
sum(stepsperday$x)/length(stepsperday$x)
```

Median:
```{r}
median(stepsperday$x, na.rm=TRUE)
```

## What is the average daily activity pattern?
```{r}
stepsperinterval <- aggregate(activ_complete$steps,list(Interval = activ_complete$interval), sum)
plot(stepsperinterval$x/length(stepsperday$x),type='l')

```

Max step interval:
```{r}
which.max(stepsperinterval$x)
```


## Imputing missing values
Total number of NAs:
```{r}
nrow(activity) - nrow(activ_complete)
```

Strategy for filling in all of the missing values in the dataset: the NAs will be replaced by zeros, since if they are not reported, then the person probably haven't done the exercises! ;)
```{r}
activity[is.na(activity)] <- 0
```
## What is mean total number of steps taken per day in the imputed dataset?
```{r}
stepsperday <- aggregate(activity$steps,list(Date = activity$date), sum)
hist(stepsperday$x, xlab='Steps per Day', main='Histogram of Steps per Day in the imputed dataset')
```

Mean total number of steps taken per day in the imputed dataset:
```{r}
sum(stepsperday$x)/length(stepsperday$x)
```

Median in the imputed dataset:
```{r}
median(stepsperday$x, na.rm=TRUE)
```

The values are of course smaller than in the first part of assignment due to the method of replacing missing values by zeros.


## Are there differences in activity patterns between weekdays and weekends?
```{r}
Sys.setlocale("LC_TIME", "English")
weekend <- c('Sat','Sun')
weekday <- c('Mon','Tue','Wed','Thu','Fri')

a <- transform(activity,Day = factor(weekdays(as.Date(activity$date),abbreviate=TRUE) %in% weekend, 
                                     labels=c('weekday','weekend')))
xyplot(steps ~ interval | Day, data = a, layout=c(1,2), type='l', ylab="Average steps per interval")

```
